Learning by Teaching a Robot:\\The Case of Handwriting

### 2015-12-17 main.tex
Minor modification in the 'ethical concerns' section

The importance of the adult is further supported by our experiments: even with
an autonomous, nominally performing robot, to put the teacher's clothes on
remains (expectedly) difficult for 5-6 years old children, and during the
experiments we conducted, the adult always played a key role at prompting the
child to give feedback to the robot or to move to the next letter or word.  At a
higher orchestration level (and as reported in the two case studies with Vincent
and Thomas), the educational scenarios were also always designed and monitored
by the adults.

>>>>

The importance of the adult is further supported by our experiments: even with
an autonomous, nominally performing robot, to put the teacher's clothes on is
not obvious for 5-6 years old children, and during the experiments we conducted,
the adult always played a key role at prompting the child to give feedback to
the robot or to move to the next letter or word.  At a higher orchestration
level (and as reported in the two case studies with Vincent and Thomas), the
educational scenarios were also always designed and monitored by the adults.
